\pdfbookmark[1]{Experimental perspective}{experimental perspective}
\chapter{Experimental discoveries of Fluxonium fabrication so far}
    % - Find all the articles where people have made Fluxonium and read about what they did. 
    % - Make a plot where you plot the coherence time/gate time/year/T_1 time as a function of year?
    % - Compare it to the theory and say what is good and what is bad about it
    The goal of this project is to fabricate a Fluxonium qubit. 
    In doing so, it wise to start where other people have left. They have spend hours working on improving small things like making gate time short, life time longer, reducing noise etc. 
    \newline
    \newline
    Here are some discussion where you compare the Theory we have for fluxonium and what you can find other groups have done in order to fabricate fluxonium experimental and based on this say something about what our starting point for fabrication should be. You can also read papers about other qubits to get inspiration about the material. or you can ask in your group what is good materials for superconducting qubits and ask if they have articles on it. 
    \newline
    \newline 
    The first Fluxonium-device was suggested by Manucharyan et al. in 2009. It was initially to remove the off-set charge of flux qubits. A flux qubit is (what are the $T_1$, $T_2$, and $T_2,echo$ times? They had the following values:
    Here are some of the things we want to look at in the experimental papers: 
        \begin{itemize}
            \item Name	
            \item Year	
            \item Life time	
            \item Gate time	
            \item $T_1$ [$\mu s$]	160
            \item $T_2$	
            \item $E_C$	
            \item $E_J$	
            \item $E_L$ 	
            \item $phi_{ext}$	3.141592654
            \item dielectric loss	0.0000002
            \item Normalized density inductor	0.000000002
        \end{itemize}
    
    \section{The first fluxonium paper - Manucharyan2009}
        The paper \textit{Fluxonium: single Cooper pair circuit free of charge offsets} is from 2009 written by Manucharyan \cite{Manucharyan2009}. This paper mention a lot of different criteria - good starting point for the fabrication of fluxonium. They made the qubit to be insensitive to offset charge which is the charge which are being accumulated in the josephson junction and can shift the energy level and lower the decoherence time. 


